### 2016-07-18 version0.0/paper3.tex
Completed paper1 and 3

The purpose of the present work is to use M31 observations to provide new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy,
as there are few studies on relations between properties of M31 with its PAH features. %generate?!
\cite{Cesarsky98} studied PAH spectra observed by ISOCAM spectro-imaging in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6$~$\mu$m emission with enhanced 11.2~$\mu$m emission. 
However,~\cite{Dim15} using {\it Spitzer}/Infrared Spectrograph~\citep[IRS;][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
Those authors re-evaluated the ISOCAM data to compare them to IRS data and found that the earlier results were likely due to incorrect background subtraction. %(PB), but the results were inconclusive. $$Sr:?
Using IRAC imaging observations,~\cite{Barmby06} found good agreement between the M31 SFR derived using observed 8~$\mu$m luminosity with other 
star formation indicators such as \halpha and far infrared luminosity.
\cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
With data mining techniques we address the question of whether,
compared to other galaxies, PAH features in M31 are unique as~\cite{Cesarsky98} claimed, or  are normal as ~\cite{Dim15} and \cite{Draine14} concluded.

@@

We describe the SOM method in $\S$~\ref{sec: method}. 
In $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
The results of the 1D SOM networks and the study of PAHs in M31 are presented in $\S$~\ref{Sec: 1d_cluster}.
In $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
In $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{Method}
\label{sec: method}
\subsection{Choosing an Algorithm}

@@

 \subsection{Self Organizing Maps}
 \label{sec: som}
 The SOM is a clustering method which reduces the dimensionality of data, while preserving topological features~\citep{Kohonen98}. 
 The results of the SOM are shown with a map of neurons, which their numbers are set by the user.
 Each neuron has a fixed position in the map and may contain one or more samples from the input data in a n-dimensional space,~\boldit{V} $\in \Re^n$.
 A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data, is associated with each node and will be varied during the training process.
 The process of creating an SOM happens over a series of $N$ iterations.
 In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,{\mathrm min}}$. 
 This neuron is the winner node and is calling Best Matching Unit (BMU). 
 In each iteration (t),The weight vectors W(t) in the neighbourhood of the BMU ($r^t_{BMU}$) will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
  \begin{equation}
            \label{equ: weight adj}
            W(t+1)=W(t)+L(t) \times R(t) \times(V(t)-W(t))
 \end{equation}
where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor with $L_0$ is the initial value of learning, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change. 
$\tau$ is the number of total iterations.
Values for the number of neurons is arbitrary, and for various toolboxes values for one or all of $L_0$,$L(t)$, $R(t)$  and $r^t_{BMU}$ are arbitrary.
~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.

@@

\subsection{Mock sample}
\label{sec: mock_sample}

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{Study Sample}
\label{Sec: data_SOMN}

@@

\begin{figure}
  \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.97\textwidth]{../image_paper3/images0.01/M31/M31.png}
        \caption{MIPS~24 $\mu$m image of M31, with positions of 10 regions studied.}
        \label{fig: regions in m31}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{../image_paper3/images0.01/M101/M101.png}
        \caption{IRAC 3.6 $\mu$m image of M101, with positions of  8 regions studied.}
    \label{fig: regions in m101}
    \end{subfigure}
    \caption{Position of the data in M31 (a) and M101 (b).}
\end{figure}

    \subsection{M31 observations}
     \label{Sec: data_M31_SOMN}

@@

    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha~(6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
     The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\mathrm TIR}$) from~\cite{Rahmani16}, and L$_{\mathrm dust}$ and dust mass from~\cite{Draine14}.

    \subsection{M101 observations}
    \label{Sec: data_M101_SOMN}

@@

      \subsection{Preparing data for data mining}

@@

    We removed all the observed data that were used to calculate galaxy properties from the input sample, to guarantee that they have not been used in multiple forms.
    To have prior knowledge of the M31 data set, 
    we computed the Pearson correlation coefficients between input measurements.
    Fig.~\ref{fig: cor_all} shows the Pearson correlation coefficients with a confidence level of 95 per cent. 
    If the significant level of correlation becomes smaller than 0.05 (5 per cent), the correlation is marked as insignificant. 
    All the PAHs correlate with one another very well.
    They are also highly correlated with the SPIRE and PACS emission, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR and metallicity.
    The fluxes from PAHs 7.7, 8.3, 12.7 and 17~$\mu$m show a weak anti-correlation with RHI.
    In general, PAHs in our data set are highly correlated with most of the other quantities.

@@

    \subsection{Clustering M31 Data}%I am not sure about it

@@

        %%%Talking about four right regions
        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH fluxes compared to the other regions (fig. 5 in \citealt{Dim15}). 
        %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
        These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
        The higher values for these quantities could be the reason that these four regions become separated from the others in the $1\times2$ network.
        Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions account for their difference in input parameters.
        Since region 10 is located in the bulge of M31 and has high surface brightness for most of the input values, regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
       % Similarities with regions 3 to 8 in the other input values (e.g. SFR) causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.

@@

    \subsection{Inside the 2 neuron network}

        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups separates for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure*}
        \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
        \caption[Pearson correlation coefficients for data from clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure*}

        Comparing the correlation coefficient plots for all 10 regions in M31 (Fig.~\ref{fig: cor_all}) and for the clustered data (Fig.~\ref{fig: cor_cluster1}) shows the differences between all 10 regions and clustered data and why regions 3 to 8 become separated from the other regions.
        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
        Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, or metallicity.
        The PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.

@@

        Correlations between PAH features and SFR, and L$_{\mathrm TIR}$ are well-studied~\citep[e.g.][]{Peeters04,Tielens08}. 
        Many groups have used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Note that, since there are only 6 regions in the clustered data, even one outlier in the data may cause the correlation coefficient to become insignificant.
        Further analyses show that the absence of correlations between PAH fluxes and SFR is because of one outlier: region 6. Region 6 is located in a FUV-bright region, which breaks the correlations. 
        When we disregard this region, high correlations between 6.2 to 17.0~$\mu$m~PAHs and SFR (and L$_{\mathrm TIR}$) reappear.

@@

        The strong anti-correlation between PAHs and stellar mass suggests that, a higher stellar mass decreases PAH emission. 
        In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, %Els: I'm unfamiliar with the details of this translation. But if you look at individual HII regions or starforming complexes, I would think that the 3.6um flux is not dominated by the stellar light as the stars are too hot to have a large fraction of emission at these wavelengths?
        and conclude that the PAH emission traces the old stellar population.
        In Fig.~\ref{fig: cor_cluster1}, we see a weak anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
        We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in the clustered data or in all 10 regions.
       % Some studies have indicated that strong stellar emission could lead to destruction of PAHs ~\citep[e.g.][]{Clayton03,Seok14}. %%% These are all UV emission
        To test that whether the anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass regions, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
        The ratio of 8/24~$\mu$m emission, which can be considered as a proxy for PAH abundances~\citep[e.g.][]{Sandstrom10,Khramtsova13}, does not anti-correlate with stellar mass for either the clustered data or all 10 regions.
        Therefore, we conclude that in our sample, stellar mass does not cause the destruction of PAHs.

@@

 %----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 2: 2D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
 \section{Two dimensional self-Organizing Maps}
 \label{sec: 2d_cluster}
    Although 1D networks are helpful to give a general idea about the data, neurons in 1D maps have a maximum of two neighbours, which can limit the usefulness of the results.
    In 2D networks, each neuron has two to six neighbours, which allows them to capture a complete picture of the complicated relations in the input data.
    Accordingly, we created $10\times10$ 2D networks to study the data in detail.
    As mentioned in previous sections, the sizes of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.

@@

            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH-only data) gradually, by adding other quantities to the input data. 
            The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e. the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and H$\alpha$ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, H$\alpha$ emission and \sii~ continuum, and so on. 
            \import{../image_paper3/text_files/image_texts/}{col3byall.tex}

@@

            Subsets, as studied in this section, can be used to learn about the effect of each input on the SOM and tell us about variation in the input data.
            Comparing Fig.~\ref{fig: only_pahs} with other networks show us that PAH features are less variable than other input data.
            These result is consistent with results from~\cite{Draine14}, who showed that the amount of PAHs in M31 for regions within 20~kpc radius. %PB: part of sentence missing?
            Additional evidence for the PAH features varying significantly less than other parameters is that changing from the PAH single band emission to total PAHs does not affect the networks.
            In contrary, PACS~100~$\mu$m, stellar mass, total gas mass and RHI
            are the data with the most variance; adding them to input data increases the dark colours between neurons significantly.
            Although with changing input parameters for each network the  distances between neurons and positions of the regions change, the general positions of the regions  relative to one another does not change dramatically. %PB: changed "data" to "regions" in this sentence - please check.
            Therefore, the networks created by subsets can be used to predict the properties of unobserved quantities in other regions of the galaxy.
            For example, photometry data, stellar mass, SFR, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, and dust mass are available for most of M31. 
            The network from Fig.~\ref{fig: wt_pahs} can be applied to 
            these data from another region in M31.
            By comparing the position of the new region with respect to our original 10 regions in the network, one would have an estimate for total PAHs in the new region without having any observational data for it.

    \subsection{Testing networks using M101 observations}
    Another application of self-organizing maps made with data from a single galaxy is to apply its trained networks on data from other galaxies to make predictions.
    To demonstrate this, we generated an SOM using only M31 measurements which were also available for M101 (Fig.~\ref{fig: subset9}a). 
    \cite{Dim15} compared PAHs in M31 with those from \hii~regions in M101, and showed the similarity between PAHs in these two galaxies (for more detail see \cite{Dim15} and \cite{Gordon08}).
    In order to test whether these similarities are limited to PAH features or can be extended to other features in these two galaxies, we applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a to M101 data (Fig.~\ref{fig: subset9}b).
    Since the neurons in the SOM network created by M31 data already have their finalized weights, the algorithm finds the minimum differences between parameters for each region in M101 and the weights of neurons and introduces the winner neuron in one iteration.
    %This process is time efficient %PB:sentence incomplete?

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{SUMMARY}
\label{sec: summary}

@@

The networks we created used values for 26 quantities from 10 regions in M31, which is not a large sample.
Increasing the dimension of the data and the number of regions would yield more reliable networks.
Since there is very little spatially-resolved PAH spectroscopy for other galaxies from the \Spitzer Space Telescope, increasing the size of samples will require data from the James Webb Space Telescope.
The method described in this work can be used to select target regions for PAH observations with that facility. %%Eh % better now?

>>>>

The purpose of the present work is to use M31 observations to provide new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy,
as there are few studies on relations between properties of M31 with its PAH features.
\cite{Cesarsky98} studied PAH spectra observed by ISOCAM spectro-imaging in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6$~$\mu$m emission with enhanced 11.2~$\mu$m emission. 
However,~\cite{Dim15} using {\it Spitzer}/Infrared Spectrograph~\citep[IRS;][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
Those authors re-evaluated the ISOCAM data to compare them to IRS data and found that the earlier results were likely due to incorrect background subtraction.
Using IRAC imaging observations,~\cite{Barmby06} found good agreement between the M31 SFR derived using observed 8~$\mu$m luminosity with other 
star formation indicators such as \halpha and far infrared luminosity.
\cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
With data mining techniques we address the question of whether,
compared to other galaxies, PAH features in M31 are unique as~\cite{Cesarsky98} claimed, or  are normal as ~\cite{Dim15} and \cite{Draine14} concluded.

@@

We describe the SOM method in $\S$~\ref{sec: method_SOMN}. 
In $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
The results of the 1D SOM networks and the study of PAHs in M31 are presented in $\S$~\ref{Sec: 1d_cluster}.
In $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
In $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Method}
\label{sec: method_SOMN}
\subsection{Choosing an Algorithm}

@@

 \subsection{Self Organizing Maps}
 \label{sec: som}
 The SOM is a clustering method which reduces the dimensionality of data, while preserving topological features~\citep{Kohonen98}. 
 The results of the SOM are shown with a map of neurons, which their numbers are set by the user.
 Each neuron has a fixed position in the map and may contain one or more samples from the input data in a n-dimensional space,~\boldit{V} $\in \Re^n$.
 A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data, is associated with each node and will be varied during the training process.
 The process of creating an SOM happens over a series of $N$ iterations.
 In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,\mathrm{min}}$. 
 This neuron is the winner node and is calling Best Matching Unit (BMU). 
 In each iteration (t),The weight vectors W(t) in the neighbourhood of the BMU ($r^t_{BMU}$) will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
  \begin{equation}
            \label{equ: weight adj}
            W(t+1)=W(t)+L(t) \times R(t) \times(V(t)-W(t))
 \end{equation}
where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor with $L_0$ is the initial value of learning, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change. 
$\tau$ is the number of total iterations.
Values for the number of neurons is arbitrary, and for various toolboxes values for one or all of $L_0$,$L(t)$, $R(t)$  and $r^t_{BMU}$ are arbitrary.
\cite{Geach12} and~\cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.

@@

\subsection{Mock Sample}
\label{sec: mock_sample}

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Study Sample}
\label{Sec: data_SOMN}

@@

    \begin{figure}
  \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.97\textwidth]{../image_paper3/images0.01/M31/M31.png}
        \caption{MIPS~24 $\mu$m image of M31, with positions of 10 regions studied.}
        \label{fig: regions in m31}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{../image_paper3/images0.01/M101/M101.png}
        \caption{IRAC 3.6 $\mu$m image of M101, with positions of  8 regions studied.}
    \label{fig: regions in m101}
    \end{subfigure}
    \caption[Position of the data in M31 and M101]{Position of the data in M31 (a) and M101 (b).}
\end{figure}

    \subsection{M31 Observations}
     \label{Sec: data_M31_SOMN}

@@

    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha~(6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
     The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_\mathrm{TIR}$) from~\cite{Rahmani16}, and L$_\mathrm{dust}$ and dust mass from~\cite{Draine14}.

    \subsection{M101 Observations}
    \label{Sec: data_M101_SOMN}

@@

     \subsection{Preparing Data for Data Mining}

@@

    We removed all the observed data that were used to calculate galaxy properties from the input sample, to guarantee that they have not been used in multiple forms.
    To have prior knowledge of the M31 data set, 
    we computed the Pearson correlation coefficients between input measurements.
    Fig.~\ref{fig: cor_all} shows the Pearson correlation coefficients with a confidence level of 95 per cent. 
    If the significant level of correlation becomes smaller than 0.05 (5 per cent), the correlation is marked as insignificant. 
    All the PAHs correlate with one another very well.
    They are also highly correlated with the SPIRE and PACS emission, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR and metallicity.
    The fluxes from PAHs 7.7, 8.3, 12.7 and 17~$\mu$m show a weak anti-correlation with RHI.
    In general, PAHs in our data set are highly correlated with most of the other quantities.

@@

    \subsection{Clustering M31 Data}

@@

        %%%Talking about four right regions
        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH fluxes compared to the other regions (fig.~5 in \citealt{Dim15}). 
        These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
        The higher values for these quantities could be the reason that these four regions become separated from the others in the $1\times2$ network.
        Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions account for their difference in input parameters.
        Since region 10 is located in the bulge of M31 and has high surface brightness for most of the input values, regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.

@@

    \subsection{Inside the Two Neuron Network}
        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups separates for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure}
        \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
        \caption[Pearson correlation coefficients for data from the clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure}

        Comparing the correlation coefficient plots for all 10 regions in M31 (Fig.~\ref{fig: cor_all}) and for the clustered data (Fig.~\ref{fig: cor_cluster1}) shows the differences between all 10 regions and clustered data and why regions 3 to 8 become separated from the other regions.
        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
        Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR, or metallicity.
        The PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.

@@

        Correlations between PAH features and SFR, and L$_\mathrm{TIR}$ are well-studied~\citep[e.g.][]{Peeters04,Tielens08}. 
        Many groups have used PAH features as a tracer of SFR by finding correlations between 
        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Note that, since there are only 6 regions in the clustered data, even one outlier in the data may cause the correlation coefficient to become insignificant.
        Further analyses show that the absence of correlations between PAH fluxes and SFR is because of one outlier: region 6. Region 6 is located in a FUV-bright region, which breaks the correlations. 
        When we disregard this region, high correlations between 6.2 to 17.0~$\mu$m~PAHs and SFR (and L$_\mathrm{TIR}$) reappear.

@@

        The strong anti-correlation between PAHs and stellar mass suggests that, a higher stellar mass decreases PAH emission. 
        In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, %Els: I'm unfamiliar with the details of this translation. But if you look at individual HII regions or starforming complexes, I would think that the 3.6um flux is not dominated by the stellar light as the stars are too hot to have a large fraction of emission at these wavelengths?
        and conclude that the PAH emission traces the old stellar population.
        In Fig.~\ref{fig: cor_cluster1}, we see a weak anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
        We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in the clustered data or in all 10 regions.

        To test that whether the anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass regions, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
        The ratio of 8/24~$\mu$m emission, which can be considered as a proxy for PAH abundances~\citep[e.g.][]{Sandstrom10,Khramtsova13}, does not anti-correlate with stellar mass for either the clustered data or all 10 regions.
        Therefore, we conclude that in our sample, stellar mass does not cause the destruction of PAHs.

@@

 %----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 2: 2D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Two-Dimensional Self-Organizing Maps}
 \label{sec: 2d_cluster}
    Although 1D networks are helpful to give a general idea about the data, neurons in 1D maps have a maximum of two neighbours, which can limit the usefulness of the results.
    In 2D networks, each neuron has two to six neighbours, which allows them to capture a complete picture of the complicated relations in the input data.
    Accordingly, we created $10\times10$ 2D networks to study the data in detail.
    As mentioned in previous sections, the sizes of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.

@@

            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH-only data) gradually, by adding other quantities to the input data. 
            The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e. the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha~emission and \sii~ continuum, and so on. 
            \import{../image_paper3/text_files/image_texts/}{col3byall.tex}

@@

            Subsets, as studied in this section, can be used to learn about the effect of each input on the SOM and tell us about variation in the input data.
            Comparing Fig.~\ref{fig: only_pahs} with other networks show us that PAH features are less variable than other input data.
            These result is consistent with results from~\cite{Draine14}, who showed that the amount of PAHs in M31 for regions within 20~kpc radius is constant.
            Additional evidence for the PAH features varying significantly less than other parameters is that changing from the PAH single band emission to total PAHs does not affect the networks.
            In contrary, PACS~100~$\mu$m, stellar mass, total gas mass and RHI
            are the data with the most variance; adding them to input data increases the dark colours between neurons significantly.
            Although with changing input parameters for each network the distances between neurons and positions of the regions change, the general positions of the regions relative to one another does not change dramatically.
            Therefore, the networks created by subsets can be used to predict the properties of unobserved quantities in other regions of the galaxy.
            For example, photometry data, stellar mass, SFR, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, and dust mass are available for most of M31. 
            The network from Fig.~\ref{fig: wt_pahs} can be applied to 
            these data from another region in M31.
            By comparing the position of the new region with respect to our original 10 regions in the network, one would have an estimate for total PAHs in the new region without having any observational data for it.

    \subsection{Applying Networks to M101 Observations}
    Another application of self-organizing maps made with data from a single galaxy is to apply its trained networks on data from other galaxies to make predictions.
    To demonstrate this, we generated an SOM using only M31 measurements which were also available for M101 (Fig.~\ref{fig: subset9}a). 
    \cite{Dim15} compared PAHs in M31 with those from \hii~regions in M101, and showed the similarity between PAHs in these two galaxies (for more detail see \cite{Dim15} and \cite{Gordon08}).
    In order to test whether these similarities are limited to PAH features or can be extended to other features in these two galaxies, we applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a to M101 data (Fig.~\ref{fig: subset9}b).
    Since the neurons in the SOM network created by M31 data already have their finalized weights, the algorithm finds the minimum differences between parameters for each region in M101 and the weights of neurons and introduces the winner neuron in one iteration.

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Summary}
\label{sec: summary}

@@

The networks we created used values for 26 quantities from 10 regions in M31, which is not a large sample.
Increasing the dimension of the data and the number of regions would yield more reliable networks.
Since there is very little spatially-resolved PAH spectroscopy for other galaxies from the \Spitzer Space Telescope, increasing the size of samples will require data from the James Webb Space Telescope.
The method described in this work can be used to select target regions for PAH observations with that facility.
